---
title: "StatMatcher"
output: flexdashboard::flex_dashboard
runtime: shiny
resource_files:
- "indagini/"
- "shiny-modules/"
---

```{r global, include=TRUE}
library(shiny)
library(flexdashboard)
library(tidyverse)
library(shinyWidgets)
library(shinydashboard)
library(StatMatch)
library(lmtest)
library(nortest)
library(corrplot)
library(rpart)
library(labelled)
library(rpart.plot)
library(plotly)
library(xtable)

ui <- shinyUI(
  fluidPage(
    dataTableOutput("data")
  )
)
options(DT.options = list(
  rownames = FALSE, scrollX = TRUE, scrollY = TRUE, pageLength = 25,fillContainer = TRUE))
#pickerOptions(style = "btn-link")
pkr_opt <- list(style = "btn", container = "body", `live-search`=TRUE)
options(shiny.maxRequestSize=1500*1024^2)
# tutto da aggiustare, nomi_indagini deve essere funzione di input
# e anche read_rds, input dipende dal contenuto della cartella indagini ......
source("shiny-modules/module_add_as_it_is.R")
source("shiny-modules/module_quant_to_cat.R")
source("shiny-modules/module_cat_to_cat.R")
source("shiny-modules/module_conta_se_vec.R")
source("shiny-modules/module_check_se_vec.R")
source("shiny-modules/module_no_trans.R")
source("shiny-modules/module_somma_vec.R")

trans_single <- c("Add as it is", "Rename variable", "Quantitative to categorical", "Recode a factor")
trans_multi <- c("Count the number of occurrences", "Check if some categories occur row-wise", "Sum row-wise")
micro_methods <- list(
  parametric = c(
    "Parametric: Conditional mean matching",
    "Parametric: Stochastic regression"),
  nonparametric = c(
    "Non-parametric: Rank Hot Deck",
    "Non-parametric: Random Hot Deck",
    "Non-parametric: Distance Hot Deck",
    "Non-parametric: Random Distance Hot Deck"),
  nonparametric_noRank = c(
    "Non-parametric: Random Hot Deck",
    "Non-parametric: Distance Hot Deck",
    "Non-parametric: Random Distance Hot Deck"),
  nonparametric_dist = c(
    "Non-parametric: Distance Hot Deck",
    "Non-parametric: Random Distance Hot Deck")
)

shiw_semp <- read_rds("indagini/shiw_2020_app_demo.rds")
hbs_semp <- read_rds("indagini/hbs_2020_app_demo.rds")
nomi_indagini <- c("SHIW-2020", "HBS-2020")
indagini1 <- list(shiw_semp, hbs_semp)
names(indagini1) <- nomi_indagini

indagini <- reactiveValues()
indagini[["SHIW-2020"]] <- shiw_semp
indagini[["HBS-2020"]] <- hbs_semp
```


Available surveys
=======================================================================

```{r child = '01-info.Rmd'}
```

Select info for matching - Recipient data {data-navmenu="Select info for matching"}
=================================================================

```{r child = '02-selezione-info-A.Rmd'}
```

Select info for matching - Donor data {data-navmenu="Select info for matching"}
=================================================================

```{r child = '02-selezione-info-B.Rmd'}
```

Data wrangling - Recipient data {data-navmenu="Data wrangling"}
=================================================================

```{r child = '03-data-wrangling-A.Rmd'}
```

Data wrangling - Donor data {data-navmenu="Data wrangling"}
=================================================================

```{r child = '03-data-wrangling-B.Rmd'}
```

Check harmonization {data-navmenu="Data wrangling"}
=================================================================

```{r child = '03-check-data-harmonization.Rmd'}
```

Selection of matching variables - Recipient data {data-navmenu="Selection of matching variables"}
=======================================================================

```{r child = '04-selection-mv-A.Rmd'}
```

Selection of matching variables - Donor data {data-navmenu="Selection of matching variables"}
=======================================================================

```{r child = '04-selection-mv-B.Rmd'}
```


Matching {data-navmenu="Macro Matching"}
=================================================================

```{r child = '05-matching-macro.Rmd'}
```

Matching {data-navmenu="Micro Matching"}
=================================================================

```{r child = '05-matching-micro.Rmd'}
```

Summaries {data-navmenu="Micro Matching"}
=================================================================

```{r child = '05-matching-micro-summaries.Rmd'}
```




