Sidebar  {.sidebar}
-----------------------------------------------------------------------

### 

```{r}
db_match_A <- reactive({
  req(X_A())
  na.omit(bind_cols(Info_A()["key_recipient"], X_A()))
})
db_match_B <- reactive({
  req(X_B())
  na.omit(bind_cols(Info_B()["key_donor"], X_B()))
})
pickerInput("Type", label = "Type of Matching", choices = c("Macro", "Micro"), selected = NULL, multiple = TRUE,
            options = pkr_opt)

# pickers selezione delle variabili (3 per macro 2 per micro)
renderUI({
  req(db_match_A())
  req(db_match_B())
  req(input$Type)
  names_all_A <- c(names(db_match_A()))[!(c(names(db_match_A()))%in%c(names(db_match_B())))]
  names_all_A <- names_all_A[!(names_all_A == "key_recipient")]
  names_all_B <-c(names(db_match_B()))[!(c(names(db_match_B()))%in%c(names(db_match_A())))]
  names_all_B <- names_all_B[!(names_all_B == "key_donor")]
  names_all <- c(names(db_match_B()))[(c(names(db_match_B()))%in%c(names(db_match_A())))]
  if(input$Type == "Macro"){
    tagList(
      pickerInput(inputId = "y_recipient", label = "Select Y from the recipient",
                  choices = names_all_A, multiple = TRUE, selected = NULL,
                  options = pkr_opt),
      pickerInput(inputId = "z_donor", label = "Select Z from the donor",
                  choices = names_all_B, multiple = TRUE, selected = NULL,
                  options = pkr_opt),
      pickerInput(inputId = "match_vars", label = "Select matching variables",
                  choices = names_all, multiple = TRUE, selected = NULL,
                  options = pkr_opt)
    )}
  else if(input$Type == "Micro"){
    tagList(
      pickerInput(inputId = "z_donor", label = "Select Z from the donor",
                  choices = names_all_B, multiple = TRUE, selected = NULL,
                  options = pkr_opt),
      pickerInput(inputId = "match_vars", label = "Select matching variables",
                  choices = names_all, multiple = TRUE, selected = NULL,
                  options = pkr_opt)
    )
    
  }
})

# pickers selezione metodo di matching
renderUI({
  req(db_match_A())
  req(db_match_B())
  req(input$Type)
  if(input$Type == "Macro"){
    req(input$y_recipient)
    req(input$z_donor)
    req(input$match_vars)
    if(is.numeric(db_match_A()[[input$y_recipient]]) && is.numeric(db_match_B()[[input$z_donor]])){
      pickerInput("macro_matching_method", label = "Parametric methods",
                  choices = c("ML", "MS"),
                  selected = NULL, multiple = TRUE,
                  options = pkr_opt)
    }
    else if(all(
      is.factor(db_match_A()[[input$y_recipient]]),
      is.factor(db_match_B()[[input$z_donor]]),
      all(sapply(db_match_B()[, input$match_vars, drop = FALSE], is.factor)))){
      pickerInput("macro_matching_method", label = "Parametric methods",
                  choices = c("Multinomial method"),
                  selected = NULL, multiple = TRUE,
                  options = pkr_opt)
    }
  }
  
  else if(input$Type == "Micro"){
    req(input$z_donor)
    req(input$match_vars)
    
    if (is.numeric(db_match_B()[[input$z_donor]])) {
      
      # Define base choices
      match_methods <- c("Parametric: Conditional mean matching",
                         "Parametric: Stochastic regression",
                         "Non-parametric: Random Hot Deck",
                         "Non-parametric: Distance Hot Deck",
                         "Non-parametric: Random Distance Hot Deck")
      
      # Check if match_vars is numeric and only one is selected
      if (length(input$match_vars) == 1 && is.numeric(db_match_B()[[input$match_vars]])) {
        match_methods <- c(match_methods, "Non-parametric: Rank Hot Deck")
      }
      
      # Create pickerInput with updated choices
      pickerInput("macro_matching_method", label = "Methods",
                  choices = match_methods,
                  selected = NULL, multiple = TRUE,
                  options = pkr_opt)
    }
    else if (is.factor(db_match_B()[[input$z_donor]])){
      pickerInput("macro_matching_method", label = "Methods",
                  choices = c("Non-parametric: Random Hot Deck","Non-parametric: Distance Hot Deck", "Non-parametric: Random Distance Hot Deck"),
                  selected = NULL, multiple = TRUE,
                  options = pkr_opt)}
  }
  
})

db_all<-reactive({
  req(input$match_vars)
  req(db_match_A(),db_match_B())
  rbind(db_match_A()[,c(input$match_vars)], db_match_B()[,c(input$match_vars)])
  
})

# se si deve usare constrained per i metodi per cui serve
renderUI({
  req(input$macro_matching_method %in% c(
    "Non-parametric: Random Hot Deck",
    "Non-parametric: Distance Hot Deck",
    "Non-parametric: Random Distance Hot Deck",
    "Non-parametric: Rank Hot Deck"))
  pickerInput(inputId = "constr", label = "Constrained",
              choices = c("Yes","No"), multiple = FALSE, selected = NULL,
              options = pkr_opt)
})

# se ci sono donation classes per i metodi per cui serve
renderUI({
  req(input$macro_matching_method %in% c(
    "Non-parametric: Random Hot Deck",
    "Non-parametric: Distance Hot Deck",
    "Non-parametric: Random Distance Hot Deck",
    "Non-parametric: Rank Hot Deck"))
  
  pickerInput(
    inputId = "STRAT",
    label = "Donation classes",
    choices = c("NO","YES"),
    multiple = FALSE,
    selected = NULL,
    options = pkr_opt
  )
})

# appare solo se ci sono sonation classes e mostra solo quelle non già scelte e non y o z
renderUI({
  req(input$STRAT == "YES")
  req(input$match_vars)
  names_all <- unique(c(names(db_match_A()), names(db_match_B())))
  lbs <- names_all[!(names_all%in%c(input$y_recipient, input$z_donor, input$match_vars))]
  pickerInput(inputId = "don_vars", label = "Select donation classes",
              choices = c(NULL,lbs), multiple = TRUE, selected = NULL,
              options = pkr_opt)
  
})

distance1 <- c("Manhattan", "Euclidean", "Mahalanobis", "minimax" )
distance2 <- c("Gower" )
distance3<- c("exact","exact matching")


renderUI({
  req(input$match_vars)
  req(input$macro_matching_method %in% c("Non-parametric: Distance Hot Deck", "Non-parametric: Random Distance Hot Deck"))
  if (all(sapply(db_match_B()[, input$match_vars, drop = FALSE], is.factor))){
    pickerInput(
      inputId = "dists",
      label = "Select a Distance",
      choices = distance3,
      multiple = FALSE,
      selected = NULL,
      options = pkr_opt
    )}
  if (all(sapply(db_match_B()[, input$match_vars, drop = FALSE], is.numeric))){
    pickerInput(
      inputId = "dists",
      label = "Select a Distance",
      choices = distance1,
      multiple = FALSE,
      selected = NULL,
      options = pkr_opt
    )}
  
  else if (all(sapply(db_match_B()[, input$match_vars, drop = FALSE], is.numeric))){
    pickerInput(
      inputId = "dists",
      label = "Select a Distance",
      choices = distance1,
      multiple = FALSE,
      selected = NULL,
      options = pkr_opt
    )}
  else {
    pickerInput(
      inputId = "dists",
      label = "Select a Distance",
      choices = distance2,
      multiple = FALSE,
      selected = NULL,
      options = pkr_opt
    )}
})


renderUI({
  #if (isTruthy(input$macro_matching_method)) {
  actionButton("btn_fai_matching", label = "Click when done", icon("paper-plane"))
  # }
})

```
Colonna produzione output {.tabset data-width=300}
-----------------------------------------------------------------------

### Output matching

```{r}
output_matching <- eventReactive(input$btn_fai_matching, {
  req(db_match_A(), db_match_B(),db_all())  # Assicura che db_match_A() e db_match_B() non siano NULL
  req(input$Type)
  req(input$macro_matching_method)  # Assicura che input$macro_matching_method esista
  req(input$z_donor)  # Controlla input essenziali
  
  # Evita errori con bottoni NULL
  cat("Matching method:", input$macro_matching_method, "\n")  # Debugging
  
  if(input$macro_matching_method == "MS"){
    req(input$y_recipient)
    req(input$match_vars)
    out <- mixed.mtc(
      data.rec = as.data.frame(db_match_A()), 
      data.don = as.data.frame(db_match_B()), 
      match.vars = input$match_vars, 
      y.rec = input$y_recipient, 
      z.don = input$z_donor, 
      method = "MS",
      rho.yz = NULL, 
      micro = FALSE, 
      constr.alg = "Hungarian"
    )
  } 
  
  if(input$macro_matching_method == "ML"){
    req(input$y_recipient)
    req(input$match_vars)
    out <- mixed.mtc(
      data.rec = as.data.frame(db_match_A()), 
      data.don = as.data.frame(db_match_B()), 
      match.vars = input$match_vars, 
      y.rec = input$y_recipient, 
      z.don = input$z_donor, 
      method = "ML",
      rho.yz = NULL, 
      micro = FALSE, 
      constr.alg = "Hungarian"
    )
  }
  
  if(input$macro_matching_method == "Multinomial method"){
    req(input$y_recipient)
    req(input$match_vars)
    #tab.x <- xtabs(paste("~", paste(c(input$match_vars), collapse = "+")), data=as.data.frame(db_all()))
    tab.x <- table(db_all()[input$match_vars])
    tab.xy <- table(db_match_A()[c(input$match_vars,input$y_recipient)])
    tab.xz <- table(db_match_B()[c(input$match_vars,input$z_donor)])
    out<-Frechet.bounds.cat(tab.x, tab.xy, tab.xz, print.f="tables", align.margins = FALSE,
                            tol= 0.001, warn = TRUE)
  }
  
  if(input$macro_matching_method %in% 
     c("Parametric: Conditional mean matching", "Parametric: Stochastic regression")){
    req(input$match_vars)
    req(input$z_donor)
    formula <- as.formula(paste(input$z_donor, "~", paste(input$match_vars, collapse = "+")))
    out <- lm(formula, data = db_match_B())
  }
  
  if(input$macro_matching_method == "Non-parametric: Random Hot Deck"){
    req(input$STRAT)
    req(input$constr)
    
    is_constrained <- ifelse(input$constr == "Yes", TRUE, FALSE)
    don_class <- NULL
    match_variables <- NULL
    if(input$STRAT == "YES"){
      req(input$don_vars)
      don_class <- input$don_vars
    }
    
    out <- RANDwNND.hotdeck(
      data.rec = as.data.frame(db_match_A()), data.don = as.data.frame(db_match_B()), 
      match.vars = match_variables, 
      don.class = don_class, 
      constrained = is_constrained) 
  }
  
  
  if(input$macro_matching_method == "Non-parametric: Rank Hot Deck"){
    req(input$STRAT)
    req(input$constr)
    don_class <- NULL
    match_variables <- NULL
    is_constrained <- ifelse(input$constr == "Yes", TRUE, FALSE)
    if(input$STRAT == "YES"){
      req(input$don_vars)
      don_class <- input$don_vars
    }
    if(isTruthy(input$match_vars)){
      match_variables <- input$match_vars
    }
    is_constrained <- ifelse(input$constr == "Yes", TRUE, FALSE)
    
    out <- rankNND.hotdeck(data.rec=as.data.frame(db_match_A()), data.don=as.data.frame(db_match_B()), var.rec=match_variables, don.class=don_class,
                           constrained=is_constrained, constr.alg="Hungarian") 
  }
  
  if(input$macro_matching_method== "Non-parametric: Distance Hot Deck"){
    req(input$STRAT)
    req(input$constr)
    req(input$dists)
    
    don_class <- NULL
    match_variables <- NULL
    is_constrained <- ifelse(input$constr == "Yes", TRUE, FALSE)
    if(input$STRAT == "YES"){
      req(input$don_vars)
      don_class <- input$don_vars
    }
    if(isTruthy(input$match_vars)){
      match_variables <- input$match_vars
    }
    
    out <- NND.hotdeck(
      data.rec = as.data.frame(db_match_A()),
      data.don = as.data.frame(db_match_B()), 
      dist.fun = input$dists, 
      match.vars = input$match_vars, 
      don.class = input$don_vars,
      constrained = is_constrained)
  }
  
  if(input$macro_matching_method == "Non-parametric: Random Distance Hot Deck"){
    req(input$STRAT)
    req(input$constr)
    req(input$dists)
    
    don_class <- NULL
    match_variables <- NULL
    is_constrained <- ifelse(input$constr == "Yes", TRUE, FALSE)
    if(input$STRAT == "YES"){
      req(input$don_vars)
      don_class <- input$don_vars
    }
    if(isTruthy(input$match_vars)){
      match_variables <- input$match_vars
    }
    
    out <- RANDwNND.hotdeck(
      data.rec = as.data.frame(db_match_A()),
      data.don = as.data.frame(db_match_B()), 
      dist.fun = input$dists, 
      match.vars = input$match_vars, 
      don.class = input$don_vars,
      constrained = is_constrained)
  }
  out
})

observeEvent(input$btn_fai_matching, {
  output$content_output <- renderUI({
    req(output_matching())
    req(input$macro_matching_method)
    
    method <- input$macro_matching_method
    
    if (method %in% c("ML", "MS")) {
      out <- renderPrint({
        output_matching()
      })
    } 
    if (method %in% c("Multinomial method")) {
      out <- renderPrint({
        output_matching()
      })
    }
    if (method %in% c("Parametric: Conditional mean matching",
                     "Parametric: Stochastic regression",
                     "Non-parametric: Random Hot Deck",
                     "Non-parametric: Distance Hot Deck",
                     "Non-parametric: Random Distance Hot Deck",
                     "Non-parametric: Rank Hot Deck")) {
      out <- DT::renderDT({
        req(matched_final())
        matched_final()
      })
    }
    out
  })
})

uiOutput("content_output")
```


### See recipient

```{r}
DT::renderDT({
  db_match_A()
})
```

### See donor
```{r}
DT::renderDT({
  db_match_B()
})
```

Summaries {data-navmenu="Matching"}
=================================================================

Colonna {.tabset data-width=300}
-----------------------------------------------------------------------

### Evaluation of the matching methods

```{r}
matched_final <- reactive({
  req(input$macro_matching_method)
  req(output_matching())
  req(db_match_A())
  req(db_match_B())
  out <- db_match_A()
  out$Z_match <- NA
  if(input$macro_matching_method %in% c("Non-parametric: Random Hot Deck","Non-parametric: Distance Hot Deck", "Non-parametric: Random Distance Hot Deck","Non-parametric: Rank Hot Deck")){
    donatore <- db_match_B()[as.numeric(output_matching()$mtc.ids[,2]), c("key_donor", input$z_donor)]
    recipiente <- db_match_A()[as.numeric(output_matching()$mtc.ids[,1]), c("key_recipient")]
    recipiente <- bind_cols(recipiente, Z_match = donatore[[input$z_donor]])
    out <- left_join(db_match_A(), recipiente)
  }
  if (input$macro_matching_method == "Parametric: Conditional mean matching" ){
    out$Z_match<-round(predict(output_matching(),db_match_A()),3)
  }
  else if ( input$macro_matching_method == "Parametric: Stochastic regression" ){
    epsilon <- rnorm(dim(db_match_A())[1], mean = 0, sd = sigma(output_matching()))
    out$Z_match<-round(predict(output_matching(),db_match_A())+epsilon,3)
  }
  out
})

eval_match <- reactive({
  req(matched_final(), db_match_B(), input$z_donor)
  out.1 <- NULL
  out.2 <- NULL
  out <- NULL
  
  # Handle numeric variables
  if (is.numeric(db_match_B()[[input$z_donor]])) {
    out<- comp.cont(
      data.A = as.data.frame(matched_final()),
      data.B = as.data.frame(db_match_B()),
      xlab.A = "Z_match",
      xlab.B = input$z_donor
    )
  }
  
  # Handle categorical variables
  if (is.factor(db_match_B()[[input$z_donor]])) {
    t.Z<-table(db_match_B()[input$z_donor])
    t.Z.sc<-table(matched_final()["Z_match"])

    out.1<- comp.prop(p1 = t.Z, p2 = t.Z.sc, n1 = nrow(matched_final()), ref = TRUE)
    
    req(input$match_vars)
    if (is.factor(db_match_B()[[input$match_vars]])) {
      t.xZ <-table(db_match_B()[c(input$match_vars,input$z_donor)])
      t.xZ.sc <-table(matched_final()[c(input$match_vars,"Z_match")])
      out.2 <- comp.prop(p1 = t.xZ, p2 = t.xZ.sc, n1 = nrow(matched_final()), ref = TRUE)
    }
    out <- list(out.1, out.2)
  }
  
  out
})

renderPrint({
  req(eval_match())
  eval_match()
})
```

### Evaluation: plot
```{r}
renderPlot({
  req(matched_final())
  req(db_match_B())
  req(output_matching())  # Ensure output_matching() is available
  if(is.numeric(db_match_B()[[input$z_donor]])){  # Ensure db_match_B_m() returns a numeric value for the selectd 
    out <- plotCont(data.A = as.data.frame(matched_final()),
                    data.B = as.data.frame(db_match_B()), xlab.A="Z_match", 
                    xlab.B=input$z_donor, w.A=NULL, w.B=NULL, type="density", ref=TRUE)}
  if(is.factor(db_match_B()[[input$z_donor]])){ 
    out <- plotTab(data.A = as.data.frame(matched_final()), 
                   data.B = as.data.frame(db_match_B()), xlab.A="Z_match", xlab.B = input$z_donor, w.A=NULL, w.B=NULL)
  }
  out
})

```
Storage and download {data-navmenu="Matching"}
=================================================================

Sidebar  {.sidebar}
-----------------------------------------------------------------------


### Save matched variable

Here you can choose to store the last obtained matched variable.

```{r}

renderUI({
  #req(matched_final())
  tagList(
    textInput("name_Z_export", "Matched variable name", value = "new_name"),
    actionButton("export_Z", "Save matched variable", icon("paper-plane"), style = "width:210px;", 
                 style="color: #fff; background-color: #337ab7; border-color: #2e6da4"),
    checkboxInput("see_whole_new", "Check if you want to see the db", value = FALSE, width = NULL)
  )
})
```

<br><br><br><br><br><br><br><br>

### Download {data-height=100}

Click here to download data. The imported recipient along with matched variables will be downloaded.

```{r}
output$downloadData <- downloadHandler(
  filename = function() { 
    paste("dataset-", Sys.Date(), ".csv", sep="")
  },
  content = function(file) {
    write.csv(DBout(), file)
  })

output$downloadUI <- renderUI( {
  downloadButton('downloadData', 'Download data', style = "width:210px;", 
                 style="color: #fff; background-color: #337ab7; border-color: #2e6da4")
})

uiOutput("downloadUI")
```
Ciccio  
-----------------------------------------------------------------------

```{r}
DBout <- reactiveVal()
kk <- reactiveVal(0)

observeEvent(input$export_Z, {
  
  if(kk() == 0){
    DBout(Ak())
    kk(1)
  }
  
  tmp <- matched_final()
  nm <- names(tmp)
  nm[nm == "Z_match"] <- input$name_Z_export
  names(tmp) <- nm
  
  if(kk()>0){
    DBout(
      left_join(
        DBout(),
        select(tmp, key_recipient, all_of(input$name_Z_export)))
    )}
  updateTextInput(session, "name_Z_export", value = "")
})
```

### Matched variables available for download

```{r}
DT::renderDT({
  req(DBout())
  if(input$see_whole_new){
    out <- DBout()
  } else {
    out <- bind_cols(DBout()$key_recipient, DBout()[!(names(DBout()) %in% names(A()))])
  }
  out
})
```

